ShabbyPages, a Robust Corpus for Training Document Image Models\thanks{Supported by Sparkfish LLC.}

### 2022-04-07 paper/shabby.tex
add author running header
update references

\institute{Sparkfish, Addison TX, USA\\\and
  SkySync, Ann Arbor MI, USA\\
  \and
  \email{ck91wei@gmail.com}}
\maketitle

@@

\section{Introduction}
Inspired by the NoisyOffice dataset~\cite{ref_url1}, we produced ShabbyPages as a way to help train, test, and calibrate computer vision machine learning algorithms designed for working with documents. We observed several limitations to the NoisyOffice dataset (namely, lack of diversity in font sizes and noise augmentations, as well as a lack of tables, graphics, form lines, etc.). Therefore, we were particularly interested in producing a dataset more appropriate for training general denoising models, so we built and leveraged the Augraphy~\cite{ref_url2} document image augmentation tool to produce noise for these images. ShabbyPages consists of  clean-noisy document image pairs.

@@

The \textit{pdftoppm} tool was used to separate each document into its constituent pages, converting these to PNGs in the process, using GNU Parallel ~\cite{ref_parallel} to distribute the job across all available cores. \texttt{parallel pdftoppm pdfs/{} pages/{} -png -r 150} took 2 minutes to process 6202 pages on a Ryzen 9 5950x.\\

From there, we used Python's \textit{cv2} library ~\cite{ref_url3} to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline. After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary. There were several possible resizing methods, but we opted to use one which simulates using a document scanner to capture an image.  Code for all of these processes is available on GitHub~\cite{ref_shabby}.

@@

\begin{thebibliography}{8}

\bibitem{ref_url1}
  UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/ml/datasets/NoisyOffice}

\bibitem{ref_url2}
  Augraphy, An augmentation pipeline for rendering synthetic paper printing, faxing, scanning and copy machine processes, \url{https://github.com/sparkfish/augraphy}

\bibitem{ref_url3}
  OpenCV, \url{https://opencv.org}

@@

>>>>

\authorrunning{A. Groleau et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sparkfish, Addison TX, USA\\\and
  SkySync, Ann Arbor MI, USA\\
  \and
  \email{ck91wei@gmail.com}}
\maketitle

@@

\section{Introduction}
Inspired by the NoisyOffice dataset~\cite{ref_noisy}, we produced ShabbyPages as a way to help train, test, and calibrate computer vision machine learning algorithms designed for working with documents. We observed several limitations to the NoisyOffice dataset (namely, lack of diversity in font sizes and noise augmentations, as well as a lack of tables, graphics, form lines, etc.). Therefore, we were particularly interested in producing a dataset more appropriate for training general denoising models, so we built and leveraged the Augraphy~\cite{ref_augraphy} document image augmentation tool to produce noise for these images. ShabbyPages consists of  clean-noisy document image pairs.

@@

The \textit{pdftoppm} tool was used to separate each document into its constituent pages, converting these to PNGs in the process, using GNU Parallel~\cite{ref_parallel} to distribute the job across all available cores. \texttt{parallel pdftoppm pdfs/{} pages/{} -png -r 150} took 2 minutes to process 6202 pages on a Ryzen 9 5950x.\\

From there, we used Python's \textit{cv2} library~\cite{ref_opencv} to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline. After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary. There were several possible resizing methods, but we opted to use one which simulates using a document scanner to capture an image.  Code for all of these processes is available on GitHub~\cite{ref_shabby}.

@@

\begin{thebibliography}{5}
\bibitem{ref_noisy}
  UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/ml/datasets/NoisyOffice}

\bibitem{ref_augraphy}
  Augraphy, An augmentation pipeline for rendering synthetic paper printing, faxing, scanning and copy machine processes, \url{https://github.com/sparkfish/augraphy}

@@

\bibitem{ref_opencv}
  OpenCV, \url{https://opencv.org}
